ECML/PKDD 2016 Discovery Challenge \\ Bank Branch Visits and Customer Acquisition Prediction using Gradient Boosted Trees

### 2016-09-08 paper/paper.tex
final

 \item Build stacking feature by predicting $testing$ and $training_1$ using original features from $N-1$ folds ($training_2$, $training_3$, $...$, $training_N$) with first stage model

>>>>

 \item Train the first stage model using data from $N-1$ folds ($training_2$, $training_3$, $...$, $training_N$) and then build the stacking feature by predicting the target variable of $testing$ and $training_1$
